Covariate analysis of HBCC RNASeq data reprocessed with STAR-feature counts workflow with Ensembl v75 (DLPFC with CQN normlaisation)

### 2017-07-22 code/Rmd/HBCC_DLPFC_STAR_ENSEMBL_v75_CQN_ModSel.Rmd
Minor changes

# Get merged metadata
METADATA_ID = 'syn4484273'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_ID
METADATA = read.csv(synGet(METADATA_ID)@filePath, fill = T, header = T, check.names = F)

@@

METADATA = METADATA %>%
  dplyr::select(Individual_ID, Institution, Gender, Age_of_Death, PMI__in_hours_, Dx, 
                DLPFC_RNA_isolation__Exclude_, DLPFC_RNA_isolation__Sample_RNA_ID, 
                DLPFC_RNA_isolation__RIN, DLPFC_RNA_report__Exclude_, DLPFC_RNA_report__Ribozero_Batch, 
                DLPFC_RNA_report__Library_Batch, DLPFC_RNA_report__Flowcell_Batch) %>%
  dplyr::rename(PMI = PMI__in_hours_, 
                IsolationExclude = DLPFC_RNA_isolation__Exclude_, 
                SampleID = DLPFC_RNA_isolation__Sample_RNA_ID, 
                RIN = DLPFC_RNA_isolation__RIN, 
                ReportExclude = DLPFC_RNA_report__Exclude_,
                RibozeroBatch = DLPFC_RNA_report__Ribozero_Batch, 
                LibraryBatch = DLPFC_RNA_report__Library_Batch, 
                FlowcellBatch = DLPFC_RNA_report__Flowcell_Batch) %>%
  dplyr::filter(SampleID %in% colnames(COUNT)) %>%
  dplyr::mutate(Tissue = 'DLPFC') %>%
  list(.,METADATA_QC) %>%
  join_all %>% droplevels() %>%
  unique %>% as.data.frame()
METADATA$SampleID = as.character(METADATA$SampleID)
```

@@

writeLines('Some control samples with Age of death less than 21 are removed')
writeLines(paste('Following',length(METADATA$SampleID[METADATA$Age_of_Death <= 21]), 'samples are removed:'))
writeLines(paste(METADATA$SampleID[METADATA$Age_of_Death <= 21], collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(Age_of_Death >= 21)
```

@@

plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  tidyr::separate(Dx.Tissue, c('Dx','Tissue'), sep = '_') %>%
  dplyr::mutate(label = SampleID)
plotdata$label[!(plotdata$SampleID %in% indToRemove)] = ''

>>>>

# Get merged metadata
METADATA_ID = 'syn2299154'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_ID
METADATA = read.csv(synGet(METADATA_ID)@filePath, fill = T, header = T, check.names = F)

@@

METADATA = METADATA %>%
  dplyr::select(Individual_ID, Institution, Gender, Age_of_Death, PMI__in_hours_, Dx, 
                DLPFC_RNA_report__Library_Batch, DLPFC_RNA_report__Ribozero_Batch, DLPFC_RNA_report__Flowcell_Batch,
                DLPFC_RNA_isolation__Exclude_, DLPFC_RNA_isolation__Sample_RNA_ID, 
                DLPFC_RNA_isolation__RIN, DLPFC_RNA_report__Exclude_, DLPFC_RNA_report__Ribozero_Batch, 
                DLPFC_RNA_report__Library_Batch, DLPFC_RNA_report__Flowcell_Batch) %>%
  dplyr::rename(LibraryBatch = DLPFC_RNA_report__Library_Batch, 
                RibozeroBatch = DLPFC_RNA_report__Ribozero_Batch, 
                FlowcellBatch = DLPFC_RNA_report__Flowcell_Batch,
                PMI = PMI__in_hours_, 
                IsolationExclude = DLPFC_RNA_isolation__Exclude_, 
                SampleID = DLPFC_RNA_isolation__Sample_RNA_ID, 
                RIN = DLPFC_RNA_isolation__RIN, 
                ReportExclude = DLPFC_RNA_report__Exclude_,
                RibozeroBatch = DLPFC_RNA_report__Ribozero_Batch, 
                LibraryBatch = DLPFC_RNA_report__Library_Batch, 
                FlowcellBatch = DLPFC_RNA_report__Flowcell_Batch) %>%
  dplyr::filter(SampleID %in% colnames(COUNT)) %>%
  dplyr::mutate(Tissue = 'DLPFC') %>%
  list(.,METADATA_QC) %>%
  join_all %>% droplevels() %>%
  unique %>% as.data.frame()
METADATA$SampleID = as.character(METADATA$SampleID)
```

@@

writeLines('Some control samples with Age of death less than 18 are removed')
writeLines(paste('Following',length(METADATA$SampleID[METADATA$Age_of_Death <= 18]), 'samples are removed:'))
writeLines(paste(METADATA$SampleID[METADATA$Age_of_Death <= 18], collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(Age_of_Death >= 18)
```

@@

plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  tidyr::separate(Dx.Tissue, c('Dx','Tissue'), sep = '_') %>%
  dplyr::mutate(label = SampleID)
plotdata$label[!(plotdata$SampleID %in% indToRemove)] = ''
plotdata$label[plotdata$Age_of_Death <= 21] = plotdata$SampleID[plotdata$Age_of_Death <= 21]
